DOpElib:\\ Differential Equations and Optimization Environment

### 2014-10-24 Examples/Documentation/introduction.tex
Typos und mini-updates in description Section 2.5

\section{Software requirements}
The library DOpE has been tested to work on both Linux and 
MAC OSX. See also the \texttt{README.OSX} file

@@

When installing \texttt{deal.II} you should take care to configure 
it to use UMFPACK, i.e.,\\
\texttt{./configure --with-umfpack}
in version up to 7.3.0. From 8.0.0 on, deal.II is compited with 
cmake, which makes the inclusion of external packages easier.

@@

\subsubsection{SNOPT}
If you would like to use the features offered in our SNOPT wrapper. You will 
need to obtain a license for \texttt{SNOPT} 
\url{http://www.sbsi-sol-optimize.com/asp/sol_product_snopt.htm}.
Unfortunately this is at present not available for free, but you should 
check if 
there is a department license already available.
For further information you should consult the file 
\texttt{ThirdPartyLibs/SNOPT.INSTALLNOTES}. In particular you need to configure 
\texttt{deal.II} with at least the following options:\\
\texttt{./configure --with-umfpack --with-blas --with-lapack}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Software requirements}
The library DOpE has been tested to work on both Linux and 
MAC OSX. See also the \texttt{README.OSX} file

@@

When installing \texttt{deal.II} you should take care to configure 
it to use UMFPACK, i.e.,\\
\texttt{./configure --with-umfpack}
in version up to 7.3.0. From 8.0.0 on, deal.II is compiled with 
cmake, which makes the inclusion of external packages easier.
Detailed installing instructions for deal.II (here the last version
8.1.0) can be found on\\ 
\texttt{http://www.dealii.org/8.1.0/readme.html}.

@@

\subsubsection{SNOPT}
If you would like to use the features offered in our SNOPT wrapper. You will 
need to obtain a license for \texttt{SNOPT} 
\url{http://www.sbsi-sol-optimize.com/asp/sol_product_snopt.htm}.
Unfortunately this is at present not available for free, but you should 
check if 
there is a department license already available.
For further information you should consult the file 
\texttt{ThirdPartyLibs/SNOPT.INSTALLNOTES}. In particular you need to configure 
\texttt{deal.II} with at least the following options:\\
\texttt{./configure --with-umfpack --with-blas --with-lapack} (up to 7.3.0)
or enabling UMFPACK in the ccmake options from version 8.0.0 on.
